---
title: "Session 3 Task"
author: "Moritz Neuhaus"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
stone_tools_data <- data.frame(
  inventory_number = c("LN15", "LN17", "LN18", "LN21", "LN23", "LN24"),
  blength = c(18, 14, 21, 14, 17, 16),
  breadth = c(9, 7, 10, 7, 8, 8),
  thickness = c(3, 2, 3, 3, 3, 2),
  material_type = c("chert", "chert", "obsidian", "chert", "obsidian", "obsidian"),
  material_provenance = c("local", "local", "local", "non-local", "local", "non-local")
)


knitr::kable(stone_tools_data)
```

```{r}
write.csv(stone_tools_data, "data/stone_tools_data.csv")
```

```{r}
stone_tools_data2 <- read.csv("data/stone_tools_data.csv")[,-1]
```

{r}
source("scripts/plotting_function.R")

plot_name <- "plots/session3_histogram_length_breadth_thickness.png"

png(plot_name, width = 700, height = 300)

three_histograms(
  variable_1 = stone_tools_data$blength,
  variable_2 = stone_tools_data$breadth,
  variable_3 = stone_tools_data$thickness,
  variable_1_main = "Histogram of count of artifacts\nby length of blade",
  variable_2_main = "Histogram of count of artifacts\nby breadth of blade",
  variable_3_main = "Histogram of count of artifacts\nby thickness of blade",
  variable_1_xlab = "Length (mm)",
  variable_2_xlab = "Breadth (mm)",
  variable_3_xlab = "Thickness (mm)"
)

dev.off()


{r}
knitr::include_graphics(plot_name)


## Length vs breadth

Create a plot displaying the relationship between length and breadth. Save it as a PNG file in “plots” subdirectory.

{r}
plot_name <- "plots/session3_scatter_length_breadth.png"

png(plot_name, width = 600, height = 400)

plot(stone_tools_data$blength, stone_tools_data$breadth)

dev.off()


{r}
knitr::include_graphics(plot_name)


## Length vs breadth vs type-provenance class

Create a plot displaying the relationship between length and breadth, this time marking (point type, colour) objects by their “type_and_provenance”. Save it as both a PNG and a EPS file in “plots” subdirectory.

{r}





---



{r}
plot_name <- "plots/session3_barplot_material_type_and_provenance_ggplot.png"

png(plot_name, width = 700)

ggplot(stone_tools_data, aes(x = type_and_provenance)) + 
  geom_bar() + 
  labs(title = "Bar plot of Blade Shape", x = "Blade Shape categories")

dev.off()


{r}
knitr::include_graphics(plot_name)

